Early Observations of the Type Ia Supernova \abc:\\ Evidence for Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-08-08 doc/ms.tex
Update title and author affiliations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{\abc}
\shortauthors{Alphabet Friends}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
\watermark{DRAFT}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Early Observations of the Type Ia Supernova \abc:\\
XXX NEED SOMETHING CLEVER TO SAY HERE XXX}

@@

\author[0000-0002-8036-8491]{Y.~Cao}
\affil{eScience Institute and Astronomy Department, University of Washington,
  Seattle, WA 98195}
\affil{Google, Mountain View, CA 94043, USA}

@@

\author{S.~Dhawan}
\affil{European Southern Observatory, Karl-Schwarzschild-Strasse 2, D-85748 Garching bei München, Germany}
\affil{Excellence Cluster Universe, Technische Universität München, Boltzmannstrasse 2, D-85748, Garching, Germany}
\affil{Physik Department, Technische Universität München, James-Franck-Strasse 1, D-85748 Garching bei München, Germany}
\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{\abc}
\shortauthors{Miller et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
\watermark{DRAFT}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Early Observations of the Type Ia Supernova \abc:\\
Evidence for Strong Ejecta Mixing and/or Interaction with Diffuse Material}

@@

\author[0000-0002-8036-8491]{Y.~Cao}
\affil{eScience Institute and Astronomy Department, University of Washington,
  Seattle, WA 98195}

@@

\author{S.~Dhawan}
\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}
